\documentclass[18pt,a4paper]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{amsmath,amsthm,amssymb,tikz-cd}
\usepackage{enumitem,amsfonts,extarrows,mathtools}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{coro}{Corollary}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definiton}[section]
\newtheorem{lemma}{Lemma}[definition]
\newtheorem{prop}{Proposition}[definition]
\newtheorem{proop}{Proposition}[section]

\tikzset{commutative diagrams/.cd,mysymbol/.style={start anchor=center,end anchor=center,draw=none}}
\newcommand\cen[2][\leq]{\arrow[mysymbol]{#2}[description]{#1}}

\makeatletter
\newcommand{\carrow}{}% just in case
\DeclareRobustCommand{\carrow}{%
	\mathrel{\vphantom{\rightarrow}\mathpalette\circle@arrow\relax}%
}

\newcommand{\circle@arrow}[2]{%
	\m@th
	\ooalign{%
		\hidewidth$#1\circ\mkern1mu$\hidewidth\cr
	$#1\longrightarrow$\cr}%
}

\begin{document}
\section{Yoneda Lemma} %{{{ Yoneda Lemma		Section
\begin{definition} %{{{Category A op		Definition
For any category $\mathcal{A} $, it's opposite category, $\mathcal{A}^{op}$
is the category having the objects of $\mathcal{A}$.
And for objects $A,B \in \mathcal{A} $, a morphism $f \in \mathcal{A}^{op} (A,B)$
only if there is a morphism $g \in \mathcal{A}(B,A)$.
\end{definition}
\begin{proop} %{{{ H_A	Definition
	For a locally small category $\mathcal{A}$, fixing an object $A \in \mathcal{A} $ gives
	a functor, $H_A: \mathcal{A} ^{op} \rightarrow Set$ defined as:
	\begin{enumerate}[label=(\roman*)]
		\item For any object $B \in \mathcal{A} $ , $H_A(B):=Hom_{Set}^{}(B,A)$
		\item For any morphism, $g : X \rightarrow Y $ in $\mathcal{A}$,
			\[H_A(g): \mathcal{A} (Y,A) \rightarrow \mathcal{A}(X,A)
				\text{ is given by } p \mapsto p \circ g\]
	\end{enumerate}
\end{proop}
\begin{definition} %{{{Presheaf Category 	Definition
	For a locally small category $\mathcal{A} $, the category of presheaves on $\mathcal{A} $, denoted by $[\mathcal{A} ^{op},Set]$
	is defined to have functors from $\mathcal{A} ^{op}$ to $Set$ as objects,
	and natural transformations between them as morphisms.
\end{definition}

%{{{ 2 Lemmas
\begin{lemma}
	Lemma 1.3.11
\end{lemma}
\begin{lemma}
	Excercise 1.3.29
\end{lemma}
%}}}

\begin{theorem}{\textbf{Yoneda Lemma}} %{{{ Yoneda		Theorem
	If $\mathcal{A} $ is a locally small category then, for any object $A \in \mathcal{A} $
	and $X \in [ \mathcal{A}^{op},Set]$,\\ there exists an isomorphism,
	\[ [ \mathcal{A} ^{op},Set ](H_A,X)\cong X(A) \text{ which is natural in } A \text{ and } X.\]
\end{theorem}

\paragraph{Notation:} \begin{itemize}
	\item We denote the category of presheaves on $\mathcal{A}$ by $\mathcal{C}$.
	\item For the map $\string ^$, instead of writing $\string ^ (a)$,
		we use $\hat{a} = b$ to denote $a \xrightarrow{ \string ^ } b$.

	\item For the map $\string ~$, instead of writing $\string ~ (a)$,
		we use $\tilde{a} = b$ to denote $a \xrightarrow{ \string ~ } b$.
	\item $[ \mathcal{A}^{op},Set](	H_A,X) $ denotes the collection of morphisms $\alpha: \begin{tikzcd}[row sep=large, column sep=huge]
				A^{op} \arrow[r,bend left=50, "H_A"{name=U, below}]
					\arrow[r, bend right = 50, "X"{name=D, above}]
					& Set
					\arrow[Rightarrow, from=U , to=D, "\alpha"]
		\end{tikzcd}$.
\end{itemize}
To prove the theorem,
first, we show that $[ \mathcal{A} ^{op}, Set](H_A,X)$ is isomorphic to $X(A) $ as set,
and then that this isomorphism is natural in $X$ and $A$.
\begin{proof}Let $\mathcal{A} $ be a locally small category.
	Fix an object $A \in \mathcal{A} $ and a presheaf $X$ on $\mathcal{A}$.

	\begin{enumerate}[label=\Roman*]
		\item \textbf{Showing isomorphism between $[\mathcal{A}^{op},Set](H_A,X)$
			and $X(A)$}\\
	Define $\string ^ :\mathcal{C}(H_A,X) \to X(A) $
	for any $\alpha:H_A \to X,$ as  $\hat{\alpha}:= \alpha_A(1_A)$.
	As $1_A \in Hom_{Set}(A,A)=H_A(A)$,
	definition of $\alpha_A$ gives that $\alpha_A(1_A)\in X(A)$
%{{{Define ~

	Define $\string ~ : X(A) \to [\mathcal{A}^{op}, Set](H_A,X)$
	for any $ x \in X(A)$ as the natural transformation $\tilde{x} : H_A \to X$ whose
	K-component is the function mapping each morphsim $p \in \mathcal{A}(K,A)$
	to $\Big(X(p)\Big)(x)$. That is, $\tilde{x}_K (p):=\Big(X(p)\Big)(x)$.\\

	We are going to show that $\tilde{x}$ is a natural transformation.
	Fix objects $K,L \in \mathcal{A} $ and morphism $q \in \mathcal{A}^{op}(K,L)$.
	$\text{Need to show that the square }
	\begin{tikzcd}
		H_A(K) \arrow[swap]{d}{\tilde{x}_K} \arrow{r}{H_A(q)}
		& H_A(L) \arrow{d}{\tilde{x}_L}\\
		X(K) \arrow[swap]{r}{X(q)}
		& X(L)
	\end{tikzcd} \text{, that is }
	\begin{tikzcd}
		\mathcal{A}(K,A) \arrow[swap]{d}{\tilde{x}_K} \arrow{r}{ - \circ q}
		& \mathcal{A} (L,A) \arrow{d}{\tilde{x}_L}\\
		X(K) \arrow[swap]{r}{X(q)}
		& X(L)
	\end{tikzcd}\text{ commutes }$.\\

	So, for any $f:K\to A$, need that $\tilde{x}_L(f \circ q)= X(q) \circ \tilde{x}_K(f)$. Using
	the definition of $\tilde{x} $ gives the following.
	\begin{align*}
	LHS &=\tilde{x}_L(f \circ q ) =\Big( X(f \circ q)\Big)(x) \\
	RHS &=X(q) \circ \tilde{x}_K(f) =\Big(X(q)\Big) \big(X(f)(x)\big)=\Big(X(q) \circ X(f)\Big) (x)
	\end{align*}
	And as $X$ is a contravariant functor, $X(f \circ q)= X(q) \circ X(f)$,
	giving that LHS=RHS.
%}}}
%{{{Isomorphism
	Now going to show that $\string ^$ and $\string ~$ define an isomorphism.
	Need to show that $\string ^ $ and $\string ~ $ are mutually inverse.
	\begin{enumerate}[label=(\roman*)]
		\item  For any $x \in X(A)$,
		$\hat{\tilde{x}}=\tilde{x}_A (1_A)=\Big(X(1_A) \Big) (x)=1_{X(A)}(x)=x$.
	\item For any $\alpha \in \mathcal{C} (H_A,X)$ , need to show that $\tilde{\hat{\alpha}}=\alpha$.
		So, it's required that each of their component are equal.
		As both $\tilde{\hat{\alpha}}$ and $\alpha$ are natural transformations
	between functors that go to the category \textit{Set}, each of the components is a function.
	So, need to show that for any $f \in \mathcal{A} (K,A)=H_A(K)$,
	$\Big(\tilde{\hat{\alpha}}\Big)_K(f)$=$\alpha_K(f)$.
	Using first the definition of $ \string ~$ and then that of $\hat{\alpha}$ gives:
	\begin{align}
	LHS=\tilde{\hat{\alpha}}_B(f)=\Big(X(f)\Big)(\hat{\alpha})=\Big(X(f)\Big)(\alpha_A(1_A))
	\end{align}
	And as $f\in \mathcal{A} (K,A)$, we also have the following.
	\begin{equation}
		RHS=\alpha_K(f)= \alpha_K(1_A \circ f)
	\end{equation}
	Because $\alpha$ is a natural transformation, the square following square commutes for $1_A$.
	\[\begin{tikzcd}
		\mathcal{A} (A,A) \arrow[swap]{d}{\alpha_A} \arrow{r}{- \circ f}
	& \mathcal{A} (K,A) \arrow{d}{\alpha_K}\\
	X(A) \arrow[swap]{r}{X(f)}
	& X(K)
	\end{tikzcd}\]
	This gives that $\alpha_K(1_A \circ f)=\Big(X(f) \Big) \big( \alpha_A (1_A) \big)$.
	Hence, we have from (1) and (2), we get that $RHS=LHS$.
	\end{enumerate}
%}}}
%{{{Naturality
\item \textbf{Showing naturality of this isomorphism }\\
By Using Lemma 1.2.1, it's enough to show that $\string ^$
is natural in $A$ for any choice of $X$, and that it is natural in $X$ for any $A$.

\begin{enumerate}[label=(\roman*)]
	\item We are going to show naturality in X. Fix any $A \in \mathcal{A}$. Need that for
		presheaves $X,Y \in \mathcal{C}$ and
		natural transformation $\beta \in \mathcal{C} (X,Y)$, the following
		square commutes.
		\begin{equation*}
		\begin{tikzcd}
			\mathcal{C}(H_A,X) \arrow[swap]{d}{ \string ^}
			\arrow{r}{\beta \circ -}
			& \mathcal{C}(H_A,Y) \arrow{d}{\string ^}\\
			X(A) \arrow[swap]{r}{\beta_A}
			& Y(A)
		\end{tikzcd}
		\end{equation*}
		So, for any $\alpha:H_A \to X$, we need that
		$\big( \string ^ \circ H_\beta \big)(\alpha) = \big( \beta_A \circ \string ^
		\big)(\alpha)$. Using definition of $H_\beta$ and $\string ^$ gives:
		\begin{align}
			LHS & = \big( \string ^ \circ H_\beta \big)(\alpha) =
			\widehat{\big(  H_\beta(\alpha)\big)}=
			\widehat{\big(  \beta \circ \alpha\big)}
			=\big(  \beta \circ \alpha\big)_A(1_A) \\
			RHS & = \big( \beta_A \circ \string ^ \big)(\alpha)
			= \beta_A (\widehat{\alpha}) =\big( \beta_A \circ \alpha_A\big)(1_A)
		\end{align}
		As $\alpha \in \mathcal{C} (H_A,X)$ and $\beta \in \mathcal{C}(X,Y)$
		are morphisms in $\mathcal{C}$, composition in $\mathcal{C}$ gives
		$(\beta \circ \alpha)_A = \beta_A \circ \alpha_A$. From (3) and (4), we
		directly get that $RHS=LHS$.

	\item We are going to show naturality in $A$. Fix any $X \in \mathcal{C} $ Need that
		for objects $A,B \in \mathcal{A} $ and morphism $f\in \mathcal{A} ^{op}(A,B)$,
		the following square commutes.
		\begin{equation*}
		\begin{tikzcd}
			\mathcal{C}(H_A,X) \arrow[swap]{d}{ \string ^}
			\arrow{r}{- \circ H_f}
			& \mathcal{C}(H_B,Y) \arrow{d}{\string ^}\\
			X(A) \arrow[swap]{r}{X(f)}
			& X(B)
		\end{tikzcd}
		\end{equation*}
		So, for any $\alpha:H_A \to X$, we need that
	$\big( \string ^ \circ H_f \big)(\alpha)=\Big((X(f)) \circ \string ^ \Big)(\alpha) $.
	Using definition of $H_f$ and $\string ^$, we get:
	\begin{align}
		LHS&=\big( \string ^ \circ H_f \big)(\alpha)= \widehat{\alpha \circ H_f}
		=(\alpha \circ H_f)_B (1_B) = \alpha_B (f \circ 1_B) = \alpha_B(1_A \circ f) \\
		RHS&=\Big((X(f)) \circ \string ^ \Big)(\alpha)
		= (X(f))(\hat{\alpha})= \Big(X(f) \Big)\big(\alpha_A(1_A)\big)
	\end{align}
	The last equality in (5) is justified because the morphism $f$ goes from $B$ to
	$A$ in $\mathcal{A} $. By using equality of (1) and (2) from I(i), for
	$f \in \mathcal{A}(B,A)$, we get that
	$\Big(X(f) \Big)\big(\alpha_A(1_A)\big)=\alpha_B( 1_A \circ f) $.
	Hence, $RHS=LHS$.
\end{enumerate}
%}}}
	\end{enumerate}
\end{proof}
\subsection{Cayley's Theorem}%
%{{{Cayley Write-up
Informally, given a locally small category$\mathcal{A} $, we can fix a presheaf $X$ on $\mathcal{A}$,
and for any object $A \in \mathcal{A} $, study the set $X(A)$ and gain information
about all possible natural transformations between $H_A$ and $X$. Moreover, by part I(ii) of the
proof of Yoneda Lemma, each of the natural transformations is determined by its action
on the identity morphisms in $\mathcal{A}$. Thus, no matter how complicated $\mathcal{A}$ is, if we choose $X$ carefully, we can hope to understand the structure of $\mathcal{A} $
by looking at how $X(A)$ changes as we vary the chosen
presheaf and object.

In group theory, Cayley's theorem says every group $G$ is isomorphic to a subgroup of the symmetric
group on G. Thus, instead of having to study a complicated group directly, we can study a subgroup of
the symmetric group on it.

Cayley's theorem and Yoneda Lemma are similar in the sense that both allow us to change the environment
that we study in by putting few restrictions on what we are allowed to study. Cayley allows us to
change setting for groups, and Yoneda does that for locally small categories.

Also, as groups themselves can be considered as small categories, we can apply Yoneda Lemma to any
group. In fact, we can get Cayley's theorem as a consequence of Yoneda Lemma by a suitable
choice of $X$ and $A$.
%}}}
\begin{definition}[Symmetric group on a set] %{{{ Symmetric group on a set	Definition
	Symmetric group on a set is the set of all bijections on X, with the binary operation
	defined as composition of bijections.
\end{definition}
\begin{theorem}{\textbf{Cayley's Theorem}} %{{{ Cayley's Theorem		Theorem
	Every group, (G,.) is isomorphic to a subgroup of symmetric group on G.
\end{theorem}
\begin{proof} Let a group $G$ be given.
	Define category $\mathcal{A} ^{op}$ as having: $\star$ as it's only object, one
	morphism for each element of $G$ and composition being as elements of $G$.
	Thus, by definition of $\mathcal{A} ^{op}$, $G\cong Hom_{\mathcal{A}^{op} }^{}(\star, \star).$
	And using the definition of $H_\star(\star)$, we get that $G \cong H_\star(\star)$.

	As $G$ is a group, $\mathcal{A}^{op}$ becomes a locally small category. Using Yoneda Lemma,
	for $\star \in \mathcal{A} ^{op}$ and functor $H_\star$, we get
	\[ [ \mathcal{A} ^{op}, Set](H_\star,H_\star) \cong H_\star(\star,\star) \cong G .\]
	where the above isomorphisms are as sets.
\end{proof}
\newpage

\subsection{Embedding of a category in Presheaf category}%{{{ Embedding		Section

\begin{definition}[Embedding of a category] %{{{ Embedding of a category		Definition
	A category, $\mathcal{A}$  is said to be embedded in a category, $\mathcal{B}$ if there exists a
	functor $F: \mathcal{A} \to \mathcal{B} $ such that $F$ is full, faithful and injective (on objects).
\end{definition} %}}}







\section{Prorelations}

\begin{definition}%{{{ Prorelation		Definition
	A prorelation is a partially ordered, down-directed, up-set of relations $X \to Y$.\\
	That is, $P \subseteq \mathcal{P}(X \times Y)$ is a prorelation if it satisfies the
	following conditions:
	\begin{enumerate}[label=(\roman*)]
		\item Partial Order: Containment of relations defines a partial order.
			That is, $r \subseteq s$  meaning that for any $(x,y) \in X \times Y$,
			if  $(x,y)\in r\;$ then $\;(x,y)\in s$.
		\item Down-directed: For any $r,s \in P$, there exists $t \in P $ such that
			$t\subseteq r \text{ and } t \subseteq s$.
		\item Up-set: For any relation $u:X\to Y$, if there exists $p \in P$ such that
			$p \subseteq u $ then $u \in P$.
	\end{enumerate}
\end{definition}
\begin{definition}%{{{ Composition of prorelations	Definition
	A prorelation $P:X \to Y$ can be composed to a prorelation $Q:Y \to Z$ by taking
	composition of the relations belonging to them. Then, the set $Q.P$ is defined as
	$\; Q.P=\{q \circ p : p \in P \text{ and } q \in Q  \}$.
\end{definition}
%{{{Composition of prorelations
\begin{lemma}
	Composition of two prorelations is a prorelation.
\end{lemma}
\begin{proof}
	For prorelations $P:X \to Y$ and $Q:Y \to Z$, need to show that Q.P is a prorelation.
	\begin{enumerate}[label=(\roman*)]
		\item (Partial Order) Inclusion of relations gives a partial order.
		\item (Down-Directed) If $k,k' \in Q.P$, then $k=q\,p$ and $k'=q'\,p'$ for some
		$q,q' \in Q$ and $p,p' \in P$. Because $Q$ and $P$ are prorelations,
		and hence down-directed sets there exists, $a \in Q$ such that
		$ a\subseteq q,q'$ and $b \in P$ such that $b \subseteq p,p'$. Thus,
		giving an element, $a\circ b$ of $Q.P$ such that $a \circ b \subseteq k, k'$.
	\item (Up-Set) Let $l:X \to Z$ be a relation, and $k \in Q.P$ such that $l \supseteq k$.
		Define relations $ p:X \to Y $ and $q:Y \to Z$ as,
		$p=\{(x,y): x \in domain(l) \text{ and } y \in Y\}$ and
		$q=\{(y,z):  y \in Y \text{ and } z \in range(l)\}$.
		Because $k\in Q.P$, there exist $q'\in Q$ and $p' \in P$ such that
		$k = q' \circ p'$. Thus by definition of $p$ and $q$, we get that
		$p \supseteq p'$ and $q \supseteq q'$. Hence $p \in P$ and $q \in Q$ because
		$P$ and $Q$ are up-sets, which gives us that $q\circ p \in Q.P$.
		For any $(x,z) \in l$, by definition
		of $p$ and $q$, we get that for every $y \in Y$, $(x,y) \in p$ and
		$(y,z) \in q $. By
		definition of composition, this gives that $(x,z) \in q \circ p$,
		giving that $l \subseteq q \circ p$. And, by definition
		of $q \circ p$ we get that $l \supseteq q \circ p$. Finally giving that
		$l=q \circ p \in Q.P$.
	\end{enumerate}
\end{proof}
%}}}
\begin{definition} %{{{ Containment of Prorelations		Definition
	For prorelations $P,Q:X\to Y$, if every relation in $Q$ is contained inside some
	relation in $P$, then $P$ is said to be contained in $Q$.
	That is $P \leq Q \;\text{ only if }\;
	\forall q \in Q, \exists p \in P \text{ such that } p \subseteq q$.
\end{definition}
\begin{definition} %{{{ Opposite relation		Definition
	For a relation $r:X \to Y$, it's opposite relation $r^o:Y \to X$ is defined as
	\[ \forall (x,y)\in X \times Y, \; (y,x) \in r^o \text{ only if } (x,y)\in r  .\]
\end{definition}
%{{{Recurring Lemmas
\begin{lemma}
	For any function $f:X \to Y$, $\; \Delta_X$ is contained in the composition $ f^o \circ f$.
\end{lemma}
\begin{proof}
	As $f$ is a function, it must be defined on every element of it's domain. Thus, for every
	$x \in X$, there exists some $(x,y)$ in $f$. By definition of $f^o$, $(y,x)$ is in $f^o$.
	Hence, by definition of composition, $(x,x)$ is in $f^o \,f$.
\end{proof}
\begin{lemma}
	For any relation $r:X \to Y$, the composition $r\circ r^o$ contains  $\subseteq \Delta_Y$.
\end{lemma}
\begin{proof}
	Suppose there exist $x \in X$ and $y \in Y$ such that
	$x\,r\,y$. By definition of $r^o$, this
	gives us that $y\, r^o \,x$. Using definition of composition,
	$y\, r^o \,x \,r\,y$ gives that	$y\, (r \circ r^o)\, y$.
\end{proof}
\begin{lemma} For relations $r,s:X\to Y$ and $t:Y\to Z$, if $\;r \subseteq s$ then $(t \circ r) \subseteq (t \circ s)$.
\end{lemma}
\begin{proof}
	Suppose relations $r,s$ and $t$ are as given above, and let $x \,(t \, r)\,z$.
	By definition of composition, there
	exists, $y \in Y$ such that $x\,r\,y$ and $y\,t\,z$.
	Using the hypothesis, as $r \subseteq  s $,
	$x\,r\,y$ gives $x\,s\,y$. And via composition of $x\,s\,y$ with $y \, t \, z $, we get
	$x\,(t\,s)\, z$. We started with any element of $(t \circ r)$ and showed that
	it must also be in $t \circ s$ and thus have that $(t \circ r) \subseteq (t \circ s)$.
\end{proof}
\begin{lemma} For relations $r:X\to Y$ and $s,t:Y\to Z$, if $s\subseteq t$ then
	$(s \circ r) \subseteq (t \circ r)$.
\end{lemma}
\begin{proof}
	Suppose relations $r,s$ and $t$ are as given above, and let  $x \,(s \, r)\,z$.
	By definition of composition of relations, we get that there exists
	some $y \in Y$ such that $x\,r\,y$ and $y\,s\,z$. Because $s \subseteq t$, $y\,s\,z$
	implies that $y\,t\,z$. Taking the composition, $x\,r\,y\,s\,z$ yields $x(t\,r)z$.
	We started with any element of $(s \circ r)$ and showed that it must also be in
	$t \circ r$ and thus have that $(s \circ r) \subseteq (t \circ r)$.


\end{proof}
%}}}

\section{Propositions}
\begin{definition} %{{{ Uniformly Continuous function 		Definition
	A function, $f:(X,A) \to (Y,B)$ is said to be uniformly continuous if $f.A \leq B.f$.
	That is, for each $b \in B$, there exists $a \in A$ such that
	$f \circ a \subseteq b \circ f$. Meaning that $
		\begin{tikzcd}
			X \cen{dr} \arrow[swap]{d}{A} \arrow{r}{f}
		& Y \arrow{d}{B}\\
		X \arrow[swap]{r}{f}
		& Y
		\end{tikzcd}
		$.
\end{definition}

\begin{definition} %{{{ Quasi-uniformity		Definition
	A prorelation on a set, $P:X \to X$ is a quasi-uniformity if it satisfies the following
	conditions:
	\begin{enumerate}[label=(\roman*)]
		\item Every relation in $P$ is reflexive. That is,
			for each $p \in P$, if $x \in X$ then $(x,x) \in p$.
		\item For each $p$ in $P$, there exists $p'$ in $P$ such that
			$p' \circ p' \subseteq p$.
	\end{enumerate}
\end{definition}
\begin{definition} %{{{Quasi-uniform space Definition
	If $X$ is a set, and $A$ is a quasi-uniformity on $X$, then (X,A) is a quasi-uniform space.
\end{definition}
%{{{ A.A=A
\begin{lemma} If $A$ is a quasi-uniformity on a set X, then $A.A=A$
\end{lemma}
\begin{proof}
	Fix any $a \in A$, as A is a quasi-uniformity, $\exists b \in A: bb \subseteq a$,
	we get that $A.A \leq A$. And as $A$ is a prorelation, and is hence down-directed,
	$\exists c \in A : a.a \supseteq c$, giving that $A.A \geq A$
\end{proof}
%}}}

%{{{ Two categories
\begin{proop} QUnif is a category defined as having quasi-uniform spaces as objects,
	and uniformly continuous maps between them as morphisms, with composition defined as that of functions.
\end{proop}
\begin{proof}
	\begin{enumerate}[label=(\roman*)]
		\item (Associativity) The composition of functions is associative by definition.
		\item (Identity) For each object $(X,A)$, define it's identity to be the identity
			function $\Delta_X:(X,A) \to (X,A)$.
			This function is uniformly continuous as $\Delta_X.A=A \leq A=A.\Delta_X$.
	\end{enumerate}
\end{proof}
\begin{definition}%{{{ Promodule		Definition
	A prorelation, $\phi:X \carrow Y$ is called a promodule $\phi: (X,A) \carrow (Y,B)$  if it
	satisfies:
	\[ \phi.A \leq \phi \text{ and } B. \phi \leq \phi \]
\end{definition}
\begin{definition} %{{{Promodule Containment 		Definition
	Containment of promodules is defined as that of prorelations.
\end{definition}
\begin{definition} %{{{ Composition of Promodules		Definition
	Promodules are composed as prorelations.\\
\end{definition}
\begin{proop}%{{{ ProMod		Definition
	ProMod is a 2-category defined as having quasi-uniform spaces as its 0-cells,
	promodules as 1-cells and containment of promodules as 2-cells.
\end{proop}
\begin{proof} In order to show that ProMod is a 2-category, need the following:
	\begin{enumerate}[label=(\alph*)]
		\item (1-Identities) For each quasi-uniform space $(X,A)$,
			define $A:(X,A) \carrow (X,A)$ to be the identity 1-cell for $(X,A)$. A is a promodule
			because $A.A=A$ (Lemma 2.2.1)
		\item (1-Composition) Need promodules to be closed under composition.\\
			Let $\phi:(X,A)\carrow (Y,B)$ and $\psi:(Y,B)\carrow (Z,C)$ be promodules.
			To show that $\psi.\phi:(X,A) \carrow (Z,C)$ is a promodule, need it to be a
			prorelation that satisfies the two conditions required to be a promodule:
			\begin{enumerate}[label=(\roman*)]
				\item By Lemma 1.2.1, prorelations are closed under composition.
					Hence, $\psi.\phi$ is a prorelation
				\item Need to show that $\psi.\phi.A \leq \psi.\phi$. So, Fix
					$p \in \psi$ and $q \in \phi$. As $\phi$ is a promodule,
					$\phi.A\leq \phi$ gives that there exists
					$ q' \in \phi \text{ and } a\in A$ such that
					$q'\,a \subseteq q$. Thus,
					$p\,q'\,a \subseteq p\,q$.
				\item Need to show that $C.\psi.\phi \leq \psi.\phi$.Fix $p \in \psi$
					and $q\in \phi$. Because
					$\psi$ is a promodule, $C.\psi \leq \psi$ gives that
					there exists $c\in C$ and $p' \in \psi$ such that
					$c\,p' \subseteq p$. Thus, $c\,p'\,q \subseteq p\,q$
			\end{enumerate}
		\item (2-Identities) As every promodule is contained in itself, always have $\psi \leq \psi$.
			Define this comparison to be the identity 2-cell for $\psi$ and denote it by $\leq_\psi$

		\item (Vertical 2-composition) For promodules $\psi,\phi,\delta:(X,A) \carrow (Y,B)$,
			if there is is a 2-cell from $\psi$ to $\phi$ and another one from $\phi$
			to $\delta$ i.e. $\psi \leq \phi \leq \delta$, then by transitivity
			of the partial order, $\psi \leq \delta$ i.e. there's a 2-cell from
			$\psi$ to $\delta$.
		\item (Horizontal 2-composition) If there are promodules
			$\psi,\psi':(X,A) \carrow (Y,B)$ and
			$\phi,\phi':(Y,B) \carrow (Z,C)$ such that $\psi \leq \psi'$ and $\phi \leq
			\phi'$, need to show that $\psi.\phi \leq \psi'.\phi'$. Fix $p' \in \psi'$ and
			$q' \in \phi'$. As $\psi\leq\psi'$, $\exists p\in \psi: p \subseteq p'$
			and as $\psi\leq\psi'$, $\exists q \in \phi: q \subseteq q'$.
			Thus, $p\,q\subseteq p'\,q'$
		\item (1-Identity) Need to show that for any promodule $\phi:(X,A) \carrow (Y,B)$,
			$\phi.A=\phi=B.\phi$. By quasi-uniformity of $A$, every $a \in A$, is
			reflexive. Thus, for any $p \in \phi$ and $a \in A$,
			$p=p. \Delta_X \subseteq p \,a$
			giving that $\phi \leq \phi.A$. And as $\phi$ is a promodule,
			$\phi \geq \phi.A$. Hence, by anti-symmetry of the partial order, $\phi=\phi.A$.

			Similarly, By quasi-uniformity of $B$, every $b \in B$, is
			reflexive. Thus, for any $p \in \phi$ and $b\in B$, $p=\Delta_Y.p\subseteq
			b\,p$ giving that $\phi \leq B.\phi$. And as $\phi$ is a promodule,
			$\phi \geq B.\phi$. Hence, $\phi=B.\phi$.
		\item (1-Associativity) As composition of relations is associative, so too is the
			composition of prorelations directly giving that composition of promodules
			i.e. 1-cells is associative.
		\item (Vertical 2-Identity) Let $\leq:\psi \to \phi$ be a 2-cell i.e.
			$\psi \leq \phi$. By our definition of identity 2-cell, $\leq_\psi.\leq_1$
			means precisely that $\psi \leq \psi \leq \phi $, and by transitivity,
			this is equivalent to $\psi \leq \phi$.
			Similarly, $\leq_1.\leq_\phi$ means exactly that $\psi
			\leq \phi \leq \phi $, and this is equivalent to $\psi \leq \phi$.
		\item (Vertical 2-Associativity) Associativity of the partial order on promodules
			directly gives the associativity of composition of 2-cells in ProMod.
		\item (Horizontal 2-Identity) Let $\psi,\phi: (X,A)\carrow (Y,B)$ be promodules.
			For any 2-cell $\leq:\psi \to \phi $, need to show that the 2-cell given
			by the horizontal composition, $\leq*\leq_A$ is equal to $\leq$, as well as
			equal to $\leq_B *\leq$. So, it's required that $\psi.A \leq \phi.A
			\iff \psi \leq \phi \iff B.\psi \leq B.\phi$. And this holds as a
			direct consequence of (f).
		\item (Horizontal 2-Associativity) As there's a unique 2-cell between any two
			promodules, and composition of promodules is associative,
			horizontal composition of 2-cells is associative.
		\item (2-Identity) For promodules $\psi:(X,A)\carrow (Y,B)$ and
			$:\phi(Y,B) \carrow (Z,C)$ need $(\leq_\psi * \leq_\phi)=\leq_{\psi.\phi}$.
			Both sides of the required equality are 2-cells $\leq:\psi.\phi
			\to \psi.\phi$.	Thus, they are equal by the uniqueness of 2-cells between
			any two 1-cells.
		\item (2-Interchange) Let $\psi,\phi,\delta:(X,A) \carrow (Y,B)$ and
			$\psi',\phi',\delta':(Y,B) \carrow (Z,C)$ be promodules. For
			2-cells $\leq_1:\psi \to \phi $,$\leq_2:\phi \to \delta $,
			$\leq_a:\psi' \to \phi' $ and $\leq_b:\phi' \to \delta'$,need to show
			$(\leq_b.\leq_a)*(\leq_2.\leq_1)=(\leq_b*\leq_2).(\leq_a*\leq_1)$.
			Both RHS and LHS are 2-cells from $\psi.\psi'$ to $\delta.\delta'$ and are
			hence equal.
	\end{enumerate}
\end{proof}
%}}}
%{{{Two functors
\begin{proop} Functor, $(-)_*:\text{QUnif} \to \text{ProMod}$ is
	defined as fixing quasi-uniform spaces (objects) and taking
	uniformly continuous functions (morphisms) to the it's pre-composition with it's domain space's identity(promodule) i.e.
	\begin{enumerate}[label=(\alph*)]
		\item for $(X,A) \in \text{QUnif}$, $(X,A)_*:=(X,A) \in \text{ProMod}$
		\item for $f:(X,A) \to (Y,B)$ in QUnif,
			$f_* := B.f$
	\end{enumerate}
\end{proop}
\begin{proof}
	We will first show that $B.f={b \circ f: b \in B}$
	is a promodule, and then that $(-)_*$ defines a functor.
	\begin{enumerate}[label=(\roman*)]
		\item (Partial-Order) Inclusion of relations acts as the partial order.
		\item (Down-Directed) Fix any $k,k'$ belonging to $B.f$. Thus, there exist
			$b,b'$ in $B$ such that $k=b\,f$ and $k'=b\,f$. Using down-directedness
			of $B$, there exists a $c \in B$ such that $c \subseteq b,b'$. Hence,
			by Lemma 2.4.4, $c\,f \subseteq k,k'$.
		\item (Up-set) Let $k$ belong to $B.f$ and $l:(X,A) \to (Y,B)$ be a
			uniformly continous function such that $l \supseteq k$.
			Define a relation $b':= \{(f(d),l(d)): d \in domain(l) \}$.
			By definition, for any $x \in X$ and $z \in Y$ such that $(x,z) \in l$, we get that
			$(f(x),z)\in b'$. And $l \supseteq k=b\, f$ implies $domain(l)  \supseteq domain(f)$
			giving $(x,f(x)) \in f$. Thus, by defniition of composition,
			$(x,z) \in b'.f$. Conversely, suppose $(x,z) \in b'.f$.
			By definition of composition, there exists $f(x)\in Y$ such that
			$(f(x),z) \in b'$. Again using the definition of
			$b'$, we get that $z=l(x)$ i.e. $(x,z)\in l$. Hence, $l=b'\, f$.
			Now we will show that $b'\supseteq b$. Because $b'\, f=l \supseteq k=b\, f$, for any
			$x\in X$ we have that $b'\big(f(x)\big) \supseteq b\big(f(x)\big)$. Thus,
			$b'|_{f(x)} \supseteq b|_{f(x)}$. By down-directedness of $B$,
			the restriction $b|_{f(x)} \subset b$ implies $ b(x)|_{f(x)} \in B$.
			Finally, $b' \supseteq b'|_{f(x)} \supseteq b|_{f(x)}$ gives $b' \in B$.
			Hence, $b'.f \in B.f$.
		\item Need to show that $(B.f).A \leq B.f$. So, fix any $b\in B$, we will find
			$b' \in B$ and $a\in A$ such that $b' \, f\,a \subseteq bf$.
			By quasi-uniformity of $B$, there exists $b' \in B$ such that $b'\,b'
			\subseteq b$. Using Lemma 2.4.3, we get that $b'\,b'\,f \subseteq b\,f$.
			As $f$ is uniformly continous, $f.A \leq B.f$ gives that there is some
			$a \in A \text{ such that } f\,a \subseteq b'\,f$. Using this in the
			previous inequality, we get $b'\,f\,a \subseteq b'\,b'\,f\subseteq  b\,f$.
		\item Need to show that $B.B.f \leq B.f$. Fix any $b \in B$, we will find
			$b' \in B$ such that $b'\,b'\,f \subseteq b\,f$.
			By quasi-uniformity of $B$, there exists $b \in B$ such that
			$b'\,b' \subseteq  b$. Using Lemma 2.4.4, we get $b'\,b'\,f \subseteq bf$.
	\end{enumerate}
	Thus, $B.f$ is a promodule. Going to show that $(-)_*$ defines a functor:
	\begin{enumerate}[label=(\roman*)]
		\item (Composition) Need to show that $(g\circ f)_*=g_*f_*$ i.e. $C.g.f=C.g.B.f$.

	In order to show $C.g.f \leq C.g.B.f$, fix any $b\in B, c\in C$.
			We will show that $c\,g\,f \subseteq c\,g\,b\,f$. As $f$ is uniformly
			continuous, $f.A \leq B.f$ gives that there exists $a \in A$ such that
			$f\,a \subseteq b\,f$. Using Lemma 2.4.3, we get $(c\,g)f\,a \subseteq
			(c\,g)b\,f$. Now, using reflexiviness of $a$, we get $c\,g\,f \subseteq
			c\,g\,b\,f$.

			Now, to show that $C.g.f \geq C.g.B.f$. Fix any $c \in X$, we will find $c' \in C$ and
			$b \in B$ such that $c\, g\, f\, \supseteq c\, g\, b\, f\, $. By quasi-uniformity of C,
			there exists $c' \in C$ such that $c \subseteq  c'\, c'$. Using Lemma 2.4.4
			gives that $c\, (g\, f)\supseteq c'\, c'\, (g\, f) $. Because $g$ is uniformly
			continuous, $C.g \geq g.B$ gives us $b\in B$ such that $g\, c' \supseteq b\, g$.
			Using this in the previous inequality gives that $c\, g\, f \supseteq c'\, g\, b\, f$.

			\item(Identity) let $(X,A)$ be in object of QUnif and
				$1_{(X,A)}:(X,A)\to(X,A)$ be the identity funtion on $(X,A)$. That is,
				$1_{(X,A)}$ is defined as $x\mapsto x$.
				Need to show that $(1_{(X,A)})_*=1_{(X,A)_*}$. Using
				functor's definition, $LHS=(1_{(X,A)})_*=A.(1_{(X,A)})=A.1_{(X,A)}=A$
				and $RHS=1_{(X,A)_*}=1_{(X,A)}$
				Using Proposition 3.2(f), we get that $A=1_{(X,A)}=RHS$.
		\end{enumerate}
\end{proof}
\begin{proop} Functor, $(-)^*:\text{QUnif}^{op} \to \text{ProMod}$ is
	defined as fixing quasi-uniform spaces and taking
	uniformly continuous functions to the composition of their opposite
	relation with it's domain space's identity i.e.
	\begin{enumerate}[label=(\alph*)]
		\item for $(X,A) \in \text{QUnif}^{op}$, $(X,A)^*:=(X,A) \in \text{ProMod}$
		\item for $f:(X,A) \to (Y,B)$ in QUnif,
			$f^* := f^o .B$
	\end{enumerate}
\end{proop}
\begin{proof}
Showing that $f^o .B: (Y,B) \carrow (X,A)$ is a promodule.\\
	So, need to show $f^o .B$ a prorelation $Y \to X$
	and that $(f^o .B).B \sqsubseteq f^o .B$ and $A.(f^o .B) \sqsubseteq f^o .B$ \\
	To show prorelation, \begin{enumerate}[label=(\roman*)]
		\item (Partial-order) Inclusion of relations i.e. for $k=f^o \circ b$ and
			$k'=f^o \circ b'$ in $f^o .B$ , $k \subseteq k' \iff b \subseteq b'$
		\item (Down directed) for $k,k' \in f^o .B$, need that $\exists l \in f^o .B
			\text{ such that } l \subseteq k,k'$

			Fix $k,k' \in f^o .B \implies \exists b,b' \in B : k=f^o \circ b \text{ and }
			k' = f^o \circ b'$

			By down-directedness of $B$, there exists $c \in B$ such that
			$ c \subseteq b,b'$, define $l=f^o \circ c$.
			Now, using Lemma 2.4.3 gives  $l= f^o \circ c \subseteq k,k'$.
		\item (Up-set) for a relation $l:Y \to X$ and $k \in f^o .B$ such that $l \supseteq k$
			, need $l \in f^o .B$

			Let $b\in B$ be such that $k=f^o \circ b$ and define
			$b':=\{(y,y'): y \in domain(l) \text{ and } y' \in (f^o)^{-1}(l(y))\}$\\
				As $l\supseteq k=f^o \circ b$, $domain(b')=domain(l)\supseteq domain(b)$
				\\ and $range(l) \supseteq range(f^o \circ b)\implies
				\forall y \in domain(b), range (b')=(f^o )^{-1}(l(y)) \supseteq (f^o)^{-1}(f^o \circ b ) = range(b)$\\
				Now, by definition of $b'$, $f^o \circ b' \supseteq l$. To show
				$f^o \circ b \subseteq l$ , \\
				$(x,y)\in f^o \circ b' \implies \exists z \in Y: (x,z)\in b' \text{ and }
				(z,y) \in f^o \implies x \in domain(l) \text{ and } z \in l(x)$ i.e.
				$(x,z) \in l$

		\end{enumerate}
	\item	To show $(f^o .B).B \leq f^o .B$, need that $\forall b \in B,
		\exists b' \in B : f^o \circ b' \circ b' \subseteq f^o \circ b$,\\
		Fix any $b \in B$, as B is a quasi-uniformity, $\exists b' \in B : b' \circ b' \subseteq b
		\implies f^o \circ b'\circ b' \subseteq f^o \circ b$

		To show $A.(f^o .B) \leq f^o .B$, need that $\forall b \in B$,
		$\exists b' \in B, a\in A : a \circ f^o \circ b' \subseteq f^o \circ b$,\\
		As $f$ is uniformly continuous, $f.A\leq B.f$ i.e. $\forall b \in B, \exists a \in A
		: f \circ a \subseteq b \circ f
		\implies a= f^o \circ f \circ a \subseteq f^o \circ  b \circ f $   \\
		Fix any $b \in B, \text{ so, } \exists b' \in B : b'b' \subseteq b$
		And, for this $b', \exists a : a \subseteq f^ob'f \implies af^ob' \subseteq f^ob'ff^ob'
		\subseteq f^o b'b' \subseteq f^o b \implies af^ob' \subseteq f^o b$\\
	\item	Now, need to show that $(-)^*$ respects composition and identity.
		\begin{enumerate}[label=(\roman*)]
			\item (Composition) let $f,g$ be uniformly continuous,
				$(X,A) \xrightarrow{f} (Y,B) \xrightarrow{g} (Z,C)$
				need that $(g \circ f)^*= f^*.g^* $

				LHS=$(g \circ f)^*=(g \circ f)^o .C=(f^o \circ g^o).C$ and
				RHS=$f^*.g^* =(f^o .B).(g^o .C)$\\
				For equality, showing that LHS$\geq$RHS and LHS$\leq$RHS:

				To show $(f^o \circ g^o).C\geq(f^o .B).(g^o .C)$, need that
				$\forall c \in C, \exists b \in B, c' \in C : f^og^oc
				\supseteq f^obgc'$ \\
				Fix any $c \in C, \text{ so, } \exists c' \in C: c' \circ c' \subseteq c
				\implies f^o g^o c \supseteq f^o g^o (c'c')
				=f^o g^o (c' \Delta_Z c') \supseteq f^o g^o c'(gg^o)c'$ \\
				By uniform conntinuity of g, for $c'\in C,\exists b\in B: gb\subseteq c'g $
				\\Thus, $f^o g^o c \supseteq f^o g^o (c'g)g^oc' \supseteq
				f^o (g^o g)bg^o c'=f^o bg^o c'$.

				To show $(f^o \circ g^o).C\leq(f^o .B).(g^o .C)$, need that
				$\forall b \in B, c \in C, \exists c' \in C: f^o g^o c \subseteq f^obg^oc $
				\\Fix any $c\in C, b\in B$ will show that $c':=c$ works:\\
				As B is a quasi-uniformity, $\Delta_Y \subseteq b\implies f^o \Delta_Y
				g^o c=f^o g^o c \subseteq f^o b	g^o c=f^o b g^o c'$
			\item(Identity) let $(X,A)\in \text{ QUnif }^{op} $, and
				$1_{(X,A)}:(X,A)\to(X,A)$ as $x\mapsto x$ need that
				$(1_{(X,A)})^*=1_{(X,A)^*}$
				LHS=$(1_{(X,A)})^*=(1_{(X,A)})^o.A=1_{(X,A)}.A=A$. \\
				And as $RHS=1_{(X,A)^*}=1_{(X,A)}$
				Using Proposition 3.2(f), we get that $A=1_{(X,A)}=RHS$.
		\end{enumerate}



	\end{proof}
	%}}}
	\begin{definition} %{{{ Fully Faithful and Dense		Definition
		Let $f:(X,A) \to (Y,B)$ be a uniformly continuous function.
		\begin{enumerate}[label=\Roman*]
			\item f is said to be fully faithful if	$f^* .f_*=A $
			\item f is said to be fully dense if $f_* .f^*=B $
		\end{enumerate}
	\end{definition}
	%NEED TO ADD TOPOLOGICALLY DENSE DEFINITION
	%Mention about topology so that below definition makes more sense ??%
%{{{ Proposition 1
	\begin{proop}
		Fix a uniformly continuous map, $f:(X,A) \rightarrow (Y,B)$
		\begin{enumerate}[label=(\alph*)]
			\item f is fully faithful if and only if $A\geq f^o.B.f$
			\item f is fully dense if and only if for any $b\in B$, $\exists b' \in B$
				such that $b' \subseteq b\,f\,f^o \,b$
			\item f is topologically dense if and only if for any $b\in B$,
				$\; b \, f\, f^o\,b$ is reflexive
			\item f is fully dense if and only if f is topologically dense
		\end{enumerate}
	\end{proop}
	\begin{proof}
	\item
		\begin{enumerate}[label=(\alph*)]
			\item \begin{enumerate}[label=(\roman*)]
				\item $ (\implies) $ Let f be fully faithful i.e. $f^*.f_*=A
					\implies f^o .B.B.f=A $\\
					Need to show that $A= f^o .B.f$ i.e.
					$A\leq f^o .B.f$ and  $A\geq f^o .B.f$\\
					By hypothesis and quasi-uniformity of B,
					$A\geq f^o .B.B.f \geq f^o B.f $\\
					To show $A \leq f^o .B.f$, need that $\forall b \in B, \exists a
					\in A : a \subseteq f^o bf$\\
					Fix $b\in B$, hypothesis gives that $f^o .B.B.f \leq A$ so, \\
					$\exists a \in A: a \subseteq f^o bbf$ and also, by
					quasi-uniformity of B, for $b, \exists b' \in B : b'b' \subseteq b
					\implies f^o b'b'f \subseteq f^o bf$\\
					Combining the above two inequalities,
					$a \subseteq f^o bbf \subseteq f^o bf$\\
				\item $(\impliedby)$ Let $A=f^o .B.f$ need to show $A=f^o.B.B.f$ i.e.
					$A\geq f^o B.B.f \text{ and } A\leq f^o B.B.f$\\
					To show $A\geq f^o .B.B.f$, need to show that $\forall a\in A,
					\exists b,b' \in B : a \supseteq f^o bb'f$\\
					Have that $A\geq f^o .B.f$ and $B.B \leq B$\\
					So, fix $a \in A$, now $\exists b\in B: a \subseteq f^o bf$
					and for this b, $\exists b'\in B: b'b' \subseteq b$.
					Therefore, $a \supseteq f^o bf \supseteq f^o b'b' f$
					To show $A\leq f^o .B.B.f$, need $\forall b,b'\in B, \exists
					a\in A : a \subseteq f^o bb'f$ \\
					Before that, uniform continuity
					of f along with Lemma 2.1.1 gives that \\$f.A\leq B.f
					\implies A=f^o f.A \leq f^o.B.f$ \\
					So, fix $b,b' \in B $, now, as ,

					$A\leq f^o .B.f $
					giving\\ $\exists a \in A : a \subseteq f^o bf$ and
					$\exists a'\in A: a' \subseteq f^o b'f \implies \Delta_X \subseteq
					f^o b'	f$.\\
					Therefore $a=a\Delta_X \subseteq (f^o bf) (f^o b'f)
					\subseteq f^o bb'f$
			\end{enumerate}
		\item	\begin{enumerate}[label=(\roman*)]
			\item $(\implies )$ Let f be fully dense i.e. $B=f_*f^* = B.f.f^o.B$.
				showing that $\forall b \in B,\exists b'\in B: b'
				\subseteq bff^ob$:\\
				So, fix $b\in B$, as $B \leq B.f.f^o.B$, there exists $b' \in
				B$ such that $b' \subseteq bff^ob$.
			\item $(\impliedby)$ Suppose $\forall b \in B, \exists b' \in B:
				b' \subseteq bff^ob$. This gives $B\leq B.f.f^o .B$, in order
				to show equality, also need $B\geq B.f.f^o .B$.
				By quasi-uniformity of B, for any $b \in B$, $\exists b'\in B:b'b'
				\subseteq b$. Now, by Lemma 2.4.2,
				\[ f f^o \subseteq \Delta_Y \implies b'f f^o b' \subseteq b'
				\Delta_Y b'=b'b' \subseteq b\]

		\end{enumerate}
	\item \begin{enumerate}[label=(\roman*)]
		\item $(\implies)$ Let f be topologically dense. We will show that
			for any $b\in B, y \in Y$, $\;(y,y) \in bff^ob$. Fix any $ b\in B$ and
			$y \in Y$. As f is topologically dense, $\overline{f(X)}=Y $, implying
			that $y\in \overline{f(X)}$, by definition giving that
			\[ \exists x\in X \text{ such that }
			(f(x),y) \in b \text{ and } (y,f(x)) \in b \]
			Re-writing the above statement in terms of relations, and
			considering f as a relation:
			\begin{align}
				(f(x),y) \in b &\text{ gives }  x(b \circ f)y \text{ i.e. }
				y \in (b \circ f)(x)\\
				(y,f(x)) \in b &\text{ gives } f(x)\subseteq b(y)
			\end{align}
			Repeatedly applying Lemma 2.4.3 to (2),
			\[ f(x) \subseteq b(y) \implies
				\big(f \circ f^o \big)(f(x) \subseteq \big(f \circ f^o \big)b(y)
				\implies \big(f \circ f^o \circ f\big)(x) \subseteq
			\big(f \circ f^o \circ b \big)(y)\]
			Applying Lemma 2.4.1 to the final inequality
			in the above statement gives that
			\[f(x)= (f\circ  \Delta_X) (x)
				\subseteq \big(f \circ f^o \circ f\big)(x) \subseteq
			\big(f \circ f^o \circ b \big)(y)  \]
			Applying Lemma 2.4.3 and then using (1) on the above inequality completes the result:
			\[ f(x) \subseteq \big(ff^ob \big)(y)
				\implies \big(b \circ f\big)(x) \subseteq
			\big(bff^ob \big)(y) \implies y \in \big(bff^ob \big)(y) \text{ i.e. } y\big(bff^ob \big)y   \]
		\item $(\impliedby)$ Fix any $y \in Y$ and $b \in B$. Also, suppose that
			$\Delta_Y \leq bff^o b$. As f is a function with domain as X,
			$f^o :Y \to X$, $\phi \neq (f^o \circ b)(y)
			\subseteq  X$. So, fix $x\in (f^o \circ b)(y)$, going to show that
			$(f(x),y)\in b$	and $(y,f(x)) \in b$. Again, while viewing f as a
			relation.
			\[ \Delta_Y \leq bff^ob
				\implies \Delta_Y(y) \subseteq bf f^o b(y)=\big(bf\big)
			(f^o b(y))\]
			Last inequality of the above statement gives $y \in (bf)(x)
			\text{ i.e. } (f(x),y)\in b $.\\
			Applying Lemma 2.4.2 to f, and then using Lemma 2.4.4,
			\begin{equation*}
				ff^o  \subseteq \Delta_Y \implies f f^o b \subseteq \Delta_Yb=b
			\end{equation*}
			Thus $f f^o b(y) \subseteq b(y)$ and hence $f(x) \subseteq b(y) \implies
			(y,f(x)) \in b$
	\end{enumerate}
\item \begin{enumerate}[label=(\roman*)]
	\item
			($\implies $) Let f be topologically dense. As B is a quasi-uniformity, for any $b \in B$,
			\begin{equation}\exists b' \in B : b'b' \subseteq b \text{ and } \Delta_Y \subseteq b'
				\implies b'=b'\Delta_Y \subseteq b'b' \subseteq b
			\end{equation}
			By the characterisation of topologically dense in (c), have that $\Delta_Y \subseteq b'f f^o b'$.
			Now, using the (3) and Lemma 2.4.3,
			\[ \Delta_Y \subseteq b'f f^o b' \implies b'=b'\Delta_Y \subseteq b'b'f f^o b' \subseteq bf f^o b'
			\subseteq bf f^o b\]
			Hence, we have $b'\in B : b' \subseteq bf f^o b$ giving us that f is fully dense (from (b)).
		\item ($\impliedby$) From (b), we have for $b \in B$, the existstence of $b' \in B$ such that $
			b' \subseteq bf f^o b$. As B is a quasi-uniformity, $\Delta_Y \subseteq b'$. So,
			$\Delta_Y \subseteq bf f^o b$, and from (c), this gives us that f is topologically dense.
	\end{enumerate}
\end{enumerate}
\end{proof}
%}}}
%{{{ A~ is a quasi-uniformity on PX
\begin{definition}%{{{ PX		Definition
	The set $PX$ is defined to be the collection of all promodules from the quasi-uniform space(X,A)
	to the quasi-uniform space 1.
	\[PX:=\{\psi : \psi:(X,A) \carrow 1 \text{ is a promodule} \}\]
\end{definition}
\begin{proop}%{{{ A~		Definition
	For any $a\in A$, $\tilde{a}$ is defined to be a relation $PX \to PX$ as
	\[ \text{ for } \phi,\psi \in PX, \; \phi \, \tilde{a} \, \psi \; \text{ only if } \;
	\phi \leq \psi.a \]
	The set, $\tilde{A}:=\{\tilde{a}:a \in A\}$ defines a quasi-uniformity on $PX$.
\end{proop}
\begin{proof}
	First need to show that $\tilde{A}$ is a prorelation,
	\begin{enumerate}[label=(\roman*)]
		\item (Partial order) For any two relations $\tilde{a},\tilde{b}:PX \to PX $,
			define $ \tilde{a} \leq \tilde{b}$ to be true only if $a \subseteq b$.
		\item(Down-Directed) Need for any $\tilde{a} ,\tilde{b} \in \tilde{A}$,
			the existstence of some $\tilde{c} \in A$ such that $c \subseteq a,b$\\
			If $\tilde{a} ,\tilde{b} \in A$ then there exist $a,b \in A$. By down-directedness
			of $A$, there exists a $c \in A$ such that  $c \subseteq a,b$. Now the definition
			of $\tilde{A}$ gives that $\tilde{c} \in \tilde{A}$. And the definition of the
			partial order on $\tilde{A}$ ensures $\tilde{c} \leq \tilde{a} ,\tilde{b}$.
		\item (Upset) For any relation $l:PX \to PX$ , need that if  $\tilde{k}$ belongs to
			$\tilde{A}$ such that $l \geq \tilde{k}$, then $l \in \tilde{A}$.\\
			Fix any $k:PX \to PX$, and $\tilde{k} \in \tilde{A}$ such that $l\geq \tilde{k} $.
			As $k$ is a relation between promodules $X \carrow 1$, it can be thought
			of as a relation $a$ on X, defined as:
			\[a:=\{(x,y): x \in domain(\psi) \text{ and }y \in domain(\phi)
			\text{ whenever } \exists \psi,\phi \in PX: \psi l \phi\}\]
			So, $l\geq \tilde{k}$ gives that $\tilde{a}\geq \tilde{k}$ i.e. $a \supseteq k.$
			And as $A$ is an upper-set, we get $a\in A$. Now, by definition of $\tilde{A}$,
			$l \in \tilde{A}$.
	\end{enumerate}
	Secondly, need show that the other two conditions hold for $\tilde{A}$,
	\begin{enumerate}[label=(\roman*)]
		\item For all $\tilde{a} \in \tilde{A}$, need $\tilde{a}$ to be reflexive i.e
			if $\psi \in PX$ then $\psi \, \tilde{a} \, \psi$.\\
			By definition of $\tilde{a}$ , need to show that $\psi \leq \psi.a$.
			So, fix a $p \in \psi$, we will show that $p \subseteq p.a$.
			Quasi-uniformity of $A$ gives that $\Delta_X \subseteq a$. Hence, by Lemma 2.4.3,
			$p=p \, \Delta_X \subseteq p \,a$ .
		\item For all $\tilde{a} \in \tilde{A}$, need to find $\tilde{b}\in \tilde{A}$ such that
			$\tilde{b}\tilde{b} \leq \tilde{a} $\\
			Before showing the result, proving that for any $x,y \in A$,
			$\tilde{x} \, \tilde{y} \leq \widetilde{xy}$
			i.e. $\forall \psi, \phi \in PX$ , $\psi(\tilde{x} \, \tilde{y})\phi \implies
			\psi \, \widetilde{xy} \, \phi $.
			If $\psi_1(\tilde{a} .\tilde{b} )\psi_3$, then, the definition of composition
			gives that $\exists \psi_2$ such that $\psi_1 \, \tilde{b} \, \psi_2 \,
			\tilde{a} \, \psi_3$. Now, the definition of $\tilde{b}$ gives $\psi_1 \leq \psi_2
			\,b$ and that of $\tilde{a}$ gives $\psi_2 \leq \psi_3 \, a$. Combining
			these inequalities, $\psi_1 \leq \psi_2.b \leq \psi_3.ab$.
			Hence, by definition of	$\widetilde{ab}$, $\psi_1 \,(\widetilde{ab})\,\psi_3$.
			Now, to show the result, fix any $\tilde{a}\in \tilde{A}$. Therefore,$a\in A$, and
			by quasi-uniformity of $A$, $\exists b \in A: b \circ b \subseteq
			a$. Thus, by the partial-order defined on $\tilde{A}$, $\widetilde{bb} \leq \tilde{a}$.
			Now, transitivity of the partial order gives us the required result,
			$ \tilde{b} \, \tilde{b} \leq \widetilde{bb} \leq \tilde{a}$.

	\end{enumerate}
\end{proof}
%}}}
%{{{ Yoneda Embedding
\begin{proop}[Yoneda Embedding]
\item For a quasi-uniform space $(X,A)$, function $y_X:X \to PX$ is defined by $x\mapsto x^*$ for $x \in X$.
	\begin{enumerate}[label=(\alph*)]
		\item $y_X:(X,A) \rightarrow (PX,\tilde{A})$ is a uniformly continuous map
		\item $y_X:(X,A) \rightarrow (PX,\tilde{A})$ is fully faithful
	\end{enumerate}
\end{proop}
\begin{proof}
\item \begin{enumerate}[label=(\alph*)]
	\item In order to show $y_X$ is uniformly continuous, need to show that $y_X.A \leq \tilde{A}.y_X $.
		By definition of $\leq$ , need $\forall a\in A, \exists b \in A:
		y_X \circ b \subseteq \tilde{a} \circ y_X $. Applying the relations
		to some element, x of the set X:
		\begin{equation} \big(y_X \circ b\big)(x) \subseteq \big( \tilde{a} \circ y_X\big)(x) \implies
		y_X(b(x)) \subseteq \tilde{a}(x^*) \end{equation}

		So, for the condition given by (4) to hold, if $y \in b(x)$, then it's required that
		$y^*=y_X(y) \in \tilde{a} (x^*)$ i.e. $x^* \tilde{a}y^*$. Using the definition of $x^*,y^*$
		and $\tilde{a}$,
		\begin{equation} x^* \tilde{a}y^* \iff x^o.A\leq y^o.A.a \iff
		\forall a' \in A, \exists a'' \in A: x^oa'' \subseteq y^oa'a  \end{equation}
		Now, fix any $a \in A$, $x\in X$. Thus, quasi-uniformity of A, gives $a'' \in A$ such that
		$a''a''\subseteq a$.Also, choose some $y \in a''(x)$. Hence, in
		order to show that the condition from (5) holds, need that
		$\forall b \in A, x^o a'' \subseteq y^oba$, and by applying the relations to an element z
		gives the following condition
		\begin{equation} \forall b \in B, \forall x \in X \text{ , }
		\big(x^oa''\big)(z) \subseteq \big(y^oba\big)(z) \end{equation}
		Examining the left side of (6),
		\[ \big( x^oa''\big)(z)=x^o (a''(z))= \begin{cases}
			\phi &\text{ if } x \notin a''(z) \\
			\star & \text{ if } \in a''(z)
		\end{cases} \]
		Thus, to show that (6) holds, need to show that (for any $b\in A$ and $z \in X$):
		\begin{equation} x \in a''(z) \implies z(y^oba)\star \text{ i.e. } y\in(ba)(z)
		\end{equation}
		To show that (7) holds, fix any $z\in X: x \in a''(z)$. Also, by our choice of $y$,
		have that $y \in a''(x)$. And as $b\in A$, it's reflexive, giving that $y \in b(y)$.
		So, by composition of relations, we get:
		\[ za''x \text{ , }  xa''y \text{ and } yby \implies z(a''a''b)y \implies z(ab)y \text{ i.e. }
		y \in (ba)(z)\]
	\item By using Proposition2.3(a), need to show that $A\geq y_X^o.\tilde{A}.y_X$ i.e. $\forall
		a\in A, \exists \tilde{b}\in \tilde{A} :  a \supseteq y_X^o \text{ } \tilde{b} \text{ } y_X $.
		Applying to an element, $x\in X$ gives the condition
		\begin{equation}
			\Big( y_X^o \text{ } \tilde{b} \text{ } y_X \Big)(x) \subseteq a(x)
			\implies \Big( y_X^o \text{ } \tilde{b} \Big) (x^*)= y_x^o
			\Big(\tilde{b}(x^*)\Big) \subseteq a(x)
		\end{equation}
		Thus, if $y^* \in PX$ such that $x^* \tilde{b} y^*$, then
		$y \in y_x^o\Big(\tilde{b}(x^*)\Big)$. Now, for (8) to hold, $y \in a(x)$ i.e. $xay$. Thus,
		need only to show that for any $a\in A, \exists b \in A $ such that $\forall x,y \in X,
		x^* \tilde{b}y^* \implies xay $. So, fix $a\in A$, and take $b \in A: bb \subseteq a$.
		Now, let $x^* \tilde{b}y^*$ i.e. $x^o.A \leq y^o .A .b$.
		Hence, $\exists c \in A: x^oc \subseteq y^o bb$. And as c is reflexive,
		\[ xcx \implies x(cx^o)\star \implies x(bby^o)\star \implies x(bb)y \implies xay \]




\end{enumerate}
\end{proof}
%}}}
%{{{ Yoneda Lemma
\begin{theorem}[Yoneda Lemma] %{{{ Yoneda Lemma		Theorem
	For every $\psi \in PX$, in the following digram,
	$\begin{tikzcd}[column sep=large ]
		X \arrow{r}{(y_X)_*}  \arrow{rd}{\psi}
  & PX \arrow{d}{\psi^*} \\
  & 1
	\end{tikzcd}$
	\begin{enumerate}[label=(\alph*)]
		\item $\psi \geq \psi^*.(y_X)^*$
		\item $\psi \in \overline{y_X(X)} \implies \psi \leq \psi^*.(y_X)_*$
	\end{enumerate}
\end{theorem}
\begin{proof}
	\begin{enumerate}[label=(\alph*)]
		\item By definition, $(y_X)_*=\tilde{A}.y_X$, and $\psi^*=\psi^o.\tilde{A}$. Need that
			$\psi \geq (y_X)_*.\psi^* = \psi^o.\tilde{A}.\tilde{A}.y_X$. And applying Lemma 2.2.1 to
			$\tilde{A}$, the required condition becomes $\psi \geq \psi^o .\tilde{A} .y_X$
			Fix $p \in \psi$,
			we will find $a \in A: p \supseteq \psi^o a y_X$. Examining the right side of the condition,
			(for any $a \in A$, $x \in X$  )
			\begin{equation} \Big(\psi^o.\tilde{a} .y_X \Big) (x) = \psi^o.\tilde{a} (x^*)=
				\psi^o\big(\tilde{a}(x^*)\big)= \begin{cases}
					\phi &\text{ if } \psi \notin \tilde{a} (x^*) \\
					\star &\text{ if } \psi \in \tilde{a} (x^*) \\

				\end{cases}\end{equation}

				In case $\psi \notin \tilde{a} (x^*)$, the condition holds trivially. As $\psi$ is a
				promodule, $\psi.A\leq \psi$ gives $\exists q\in \psi, a
				\in A: qa \subseteq p$. Thus, fix $x\in X$ and	$\psi \in PX$ such that
				$x^* \tilde{a} \psi $. We will now show that $xp\star$. Using the definition of $\tilde{a}$,

				\begin{equation} x^* \tilde{a} \psi \implies x^o.A \leq \psi.a
					\implies \exists b\in A: x^ob \subseteq qa
					\implies \forall z \in X, \big(x^o b \big)(z) \subseteq (qa)(z)
				\end{equation}
				Thus, in particular for $z=x$, as $b$ is reflexive, $xbx$, which gives:
				\begin{equation} \big(x^o b \big)(x) \subseteq (qa)(x) \implies x^ox \subseteq (qa)(x) \implies \star \in (qa)(x) \end{equation}
				But, as $qa \subseteq p$ , (11) gives that $xp\star$.
			\item Suppose $\psi \in \overline{y_X(X)}$, need to show $\psi \leq \psi^*.(y_X)_*=\psi^o.\tilde{A}.y_X$ i.e.
				for $a \in A,$ $\exists p \in \psi: p \subseteq \psi^o.\tilde{a}.y_X$. For any $x \in domain(p)$,
				the condition requires:
				\begin{equation}
					p(x) \subseteq  \psi^o.\tilde{a} .y_X(x)=\psi^o\big(\tilde{a} (x^*)\big)
				\end{equation}
				By definition of $p$, for (12) to hold, need that $xp\star \implies \psi \in \tilde{a}(x^*) $. Fix
				any $a\in A$, we will find $p \in \psi$ such that (12) holds. By quasi-uniformity of A,
				$\exists b \in A: bb \subseteq a$. From Proposition 2.5(a), $y_X$ is uniformly continuous,
				$y_X.A \leq \tilde{A}.y_X $ giving that $\exists c \in A: y_xc \subseteq \tilde{b}y_X $. Thus, for
				any $z,w\in X$ such that $z c w$,
				\begin{equation} \big(y_X c \big)(z) \subseteq \big(\tilde{b} y_X\big)(z) \implies
					y_X(c(z)) \subseteq \tilde{b}(z^*) \implies w^* \in \tilde{b}(z^*) \text{ i.e. } z^* \tilde{b} w^*
				\end{equation}
				As $A$ is a quasi-uniformity, $\exists d\in A: dd \subseteq c$. Also, because $A$ is a down-
				directed set, $\exists a' \in A: a' \subseteq b,d $. This along with (13) gives that
				for any $x,y \in X$
				\begin{equation} x(a'a')y \implies x(dd)y \implies xcy \implies x^* \tilde{b} y^* \end{equation}
				Now, because $\psi \in \overline{y_X(X)}$, we get
				$\exists x^* \in y_X(X) \text{ such that } \psi \tilde{a'}x^* \text{ and } x^* \tilde{a'} \psi $.
				By definition of $\tilde{a}$, $\psi \tilde{a'}x^*$ gives
				\begin{equation} \psi \leq x^o.A.a' \implies \exists p \in \psi: p \subseteq x^o a'a' \end{equation}
				Fix any $z \in X : zp \star$, using (15) and (14) gives:
				\begin{equation} zp \star \xRightarrow z(x^o a'a') \star \xRightarrow{(15)} z(a'a')x
				\xRightarrow{(14)} z^* \tilde{b}x^*   \end{equation}

				Finally, by definition of the partial order on $\tilde{A}$,$a' \subseteq b \implies \tilde{a'}
				\subseteq \tilde{b} $. Therefore,  $x^* \tilde{a'}\psi \implies x^* \tilde{b}\psi$.
				Now, using (16), $z^* \tilde{b}x^* \text{ and } x^*\tilde{b}\psi  $ gives the desired result
				$z^* \tilde{b} x^* $.
		\end{enumerate}
	\end{proof}
	%}}}
	%}}}
	%{{{ Yoneda Corollary NOT COMPLETE YET
	\begin{coro}
		For $\psi \in PX$, $\psi \in \overline{y_X(X)}$ if and only if $\psi$ is a right-adjoint.
	\end{coro}
	\begin{proof}	Fix any $\psi \in PX$. \setcounter{equation}{0}
		\begin{enumerate}[label=(\roman*)]
			\item ($\implies$)

			\item ($\impliedby$) Suppose $\psi$ is a right adjoint. Need to show that for any
				$a \in A$, $\exists x^* \in y_X(X)$ such that $\psi \, \tilde{a} \,x^*
				\tilde{a} \, \psi$. Fix $a \in A$. Because $\psi$ is a right-adjoint, there
				exists a promodule $\phi: 1 \carrow X$ such that $\phi.\psi \leq A$ and
				$1\leq \psi.\phi$. From $\phi.\psi \leq A$, we get that
				\begin{equation}\exists p \in \phi, q \in \psi \text{ such that }
					a \supseteq p.q
				\end{equation}
				Because $\phi$ and $\psi$ are promodules,
				\begin{align}
					A.\phi \leq \phi & \text{ gives the existence of } p' \in \phi \text{ such that } p\supseteq a'p'  \\
					A.\psi \leq \psi & \text{ gives the existence of } q' \in \psi \text{ and } a'' \in A
					\text{ such that } q \supseteq a''q'
				\end{align}
				Now, from $1 \leq \psi.\phi$, we get that $q'\,p'$ is reflexive i.e. $\star (q' \,p')
				\star$. By the definition of composition we get the existence of an $x \in X$
				such that $\star \, p' \, x \,q'\,\star$. Now, considering $x$ as a map, $x:1 \to X$
				defined as $\star \mapsto x$,
				\begin{align}
					x \, q' \, \star \text{ i.e. } &\star \in q'(x) \text{ gives that }
					q' \supseteq x^o \\
					\star \,p' \, x \text{ i.e. } &x \in p'(\star) \text{ gives that }
					p'\supseteq x
				\end{align}
				Thus, by using inequalities (1),(2) and (3), we get that
				\begin{equation}
					a \supseteq p\,q \supseteq a'\,p'\,q'\,a''
				\end{equation}
				By definition of $\tilde{a}$, to show $\psi \, \tilde{a} \, x^*$,
				we need that $\psi \leq x^*\,a=x^o.\,A.\,a$. Showing
				$\text{ for any } b\in A$, $\;  x^o\,b\,a \supseteq q'$:
				\[ x^o\,b\,a \supseteq x^o\,b\,a'\,p'\,q' \supseteq x^o\,b\,a'\,x\,q'
				\supseteq x^o\,x\,q' \subseteq q'\]
				Where the first inequality comes from (6) by using reflexiviness of $a''$ and then
				left-multiplying by $x^o$. The second inequality comes from (5),
				third one from reflexiviness of $b$ and $a'$,
				and the last one is given by Lemma 2.4.1.

				In order to show $x^* \, \tilde{a} \, \psi$, by definition of $\tilde{a}$,
				need that $x^o.A=x^* \leq \psi\,a$. Fix $k\in \psi$. We will show
				$k\,a \supseteq x^o \, a''$.

				\begin{equation}
					a\supseteq a'\,p'\,q'\,a'' \supseteq p'\,q'\,a''
					\supseteq p' \,x^o \,a''
				\end{equation}

				Where the first inequality is given by (6), second one
				is due to reflexiviness	of $a'$ and the third inequality comes by using (4).
				Left-multiplying (7) with $k$ gives
				\begin{equation}
					ka \supseteq k\,p'\,x^o\,a''
				\end{equation}
				FINAL STEP LEFT !!
\end{enumerate}
	\end{proof}
	%}}}
	\end{document}
